The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-10-17 Paper.qmd
Added code to present minimum spanning tree in paper.

>>>>

::: {#fig-mst}
```{r}
include_graphics("Figures/plot_mst.pdf")
```

Minimum spanning tree of child signaling and variables thought to cause differences in signaling strategies. Blue edges = negative [do we want more detail here? e.g., partial correlations or w/e the proper Bayesian way to word that is] correlations between variables. Red edges = positive correlations between variables. Edge lengths represent [check that this is right and if more specificity is needed] distances between variables. Line weights represent(1 - correlation coefficient)
:::
